The language of generalization: Probability, vagueness, and interaction

### 2018-02-22 paper/case1-generics.Rmd
address ellens inline comments in intro and expts

Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propagation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday reasoning.
In addition, generics have been the case study of choice for the semantics of the language of generalization because of their vexing similarity to quantified statements (e.g., "Most dogs bark").
Time after time, psychologists have shown that generics simply do not reduce to quantified statements [e.g., @Khemlani2012, @Prasada2013, @Cimpian2010].

Here, we take our first empirical look at how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions [@Prasada2013]: *majority characteristic* (e.g., "Ducks have wings."),  *minority characteristic* (e.g., "Robins lay eggs."), *striking* (e.g. "Mosquitos carry malaria."),  *false generalization* (e.g., "Robins are female."), and *absent features* (e.g. "Lions lay eggs.").
We further craft sentences to elicit the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high referent-prevalence (Expt. 1a).
We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(p_{fk})$ (Expt. 1b).
This elicitation procedure includes measurements of the referent-category feature-probabilities $p_{fk'}$  (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq. \ref{eq:S1}) as well as for simpler, alternative models.

@@

```{r generics-prior-task, fig.cap="Prior elicitation task. A: Participants first generated animal names after seeing six example categories. B: One feature at a time, participants estimated the percentage of the category with the feature, for each category.", fig.height = 3}
fig.priors.expt.stage1 <- ggdraw() + draw_image(paste(project.path, "paper/figs/generics-prior-stage1.jpeg", sep=""), scale = 1)
fig.priors.expt.stage2 <- ggdraw() + draw_image(paste(project.path, "paper/figs/generics-prior-stage2.jpeg", sep=""), scale = 1)

@@

```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 6, fig.cap="A: Empirically elicited prior distributions over prevalence for eight properties. B: Cumulative density plots reveal that a model of a mixture of two Beta distributions does substantially better at capturing the structure of the priors than a single Beta distribution. Distributions are the posterior predictive distributions for the models of the prio and the raw empirical distribution. A completely uniform distribution would be represented as the y = x line."}
load('../analysis/generics-priors-posteriorPredictives.Rdata')

@@

Cue validity is linearly related to a point-estimate of the prevalence prior distribution (see Model section and Appendix A).
It thus implicitly captures information about other categories, though cannot capture the structure that is present in the prevalence priors.
To show that this structure is important, we explore a secondary baseline model based on prevalence and cue validity.

@@

Though the cue validity of a particular (category, property) pair can be derived from the prevalence prior distribution, previous empirical studies of generic language have not done this.
Instead, these studies estimate cue validity by asking a separate group of participants about the distinctiveness of features for given animals [e.g., @Khemlani2012], though different studies use different measurements. 
Preliminary analysis of these different measurements revealed that a *free production* paradigm [@Cree2006] is preferred.
Participants ($n = 100$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
For a detailed analysis of different cue validity measurements and comparison to *prevalence prior derived cue validity*, see Appendix B.

@@

In explaining the variable endorsements of generics, we related the referent-category prevalence (e.g., the percentage of robins that lay eggs) to the endorsement of the generalization (e.g., "Robins lay eggs") via the prevalence priors (e.g., the percentage of different kinds of animals that lay eggs). 
In doing so, we used generic statements about familiar animal categories, which has long been the cleanest domain for testing semantic theories of generics by providing minimal comparison like "Robins lay eggs" vs. "... are female". 
To model statements about familiar categories, we were forced to *measure* the relevant quantities in the model (i.e., the referent prevalence and the prevalence priors), which people have access to via their mental representations of the category. 
We now seek to demonstrate how these quantities are causally related to endorsement, by manipulating referent prevalence (Case 2) and feature-probability priors (Case 3).
In addition, we take this opportunity to highlight the generality of the theory, by performing these additional empirical tests in different domains for generalization: events and causes.

>>>>

Generalizations about categories (i.e., *generic language*; e.g., "Dogs bark.") have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propagation [@Rhodes2012], motivation [@Cimpian2007], and many other facets of everyday reasoning.
In addition, generics have been the case study of choice for the semantics of the language of generalization because of their tantalizing similarity to quantified statements (e.g., "Most dogs bark").
However, intuitions and empirical data argue that generics simply do not reduce to quantified statements [e.g., @Khemlani2012, @Prasada2013, @Cimpian2010].

Here, we take our first empirical look at how the *underspecified threshold* endorsement model predicts actual human endorsements of generic statements.
We measure endorsement for thirty generic sentences that cover a range of conceptual distinctions previously discussed in the empirical literature on generics [@Prasada2013]: characteristic features displayed by a majority (e.g., "Ducks have wings."),  characteristic features displayed by a minority (e.g., "Robins lay eggs."), features that are *striking* or *dangerous* (e.g. "Mosquitos carry malaria."),  noncharacteristic features displayed by a minority (e.g., "Robins are female."), and features that are totally absent (e.g. "Lions lay eggs.").
We further craft sentences with the goal of eliciting the full range of acceptability judgments (intuitively: "true", "false", and "indeterminate") for generics with properties of low, medium, and high referent-prevalence (Expt. 1a).
We examine generics about animal categories in order to reliably measure the prior belief distribution over the prevalence of features $P(p_{fk})$ (Expt. 1b).
This elicitation procedure includes measurements of the referent-category feature-probabilities $p_{fk'}$  (e.g.,$P(x \text{ lays eggs} \mid x \text{ is a robin})$), allowing us to both generate predictions for the endorsement model (Eq. \ref{eq:S1}) as well as for simpler, alternative models.

@@

```{r generics-prior-task, fig.cap="Prior elicitation task. A: Participants first generated animal names after seeing six example categories. B: One feature at a time, participants estimated the percentage of the category with the feature, for each category.", fig.height = 3, cache = F}
fig.priors.expt.stage1 <- ggdraw() + draw_image(paste(project.path, "paper/figs/generics-prior-stage1.jpeg", sep=""), scale = 1)
fig.priors.expt.stage2 <- ggdraw() + draw_image(paste(project.path, "paper/figs/generics-prior-stage2.jpeg", sep=""), scale = 1)

@@

```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 6, fig.cap="A: Empirically elicited prior distributions over prevalence for eight properties. B: Cumulative density plots reveal that a model of a mixture of two Beta distributions does substantially better at capturing the structure of the priors than a single Beta distribution. Distributions are the posterior predictive distributions for the models of the prio and the raw empirical distribution. A completely uniform distribution would be represented as the y = x line.", cache = F}
load('../analysis/generics-priors-posteriorPredictives.Rdata')

@@

Cue validity is a metric of how diagnostic the feature is of the kind, and is given formally by the probability of a kind given the feature $P(k \mid f)$.
As discussed in the Computational Model section above, cue validity is linearly related to expected value of the prevalence prior distribution (see Appendix A for derivation).
Cue validity can thus be seen as a *point estimate* of the prevalence prior distribution, a single metric that collapses across the full distribution.

To show that the full distribution over prevalence is important, we explore a secondary baseline model based on prevalence and cue validity.
Though the cue validity of a particular category by a particular property can be derived from the prevalence prior distribution, previous empirical studies have estimated cue validity in various ways from empirical data about distinctiveness [@Cree2006; @Khemlani2012].
In the empirical literature on generics, researchers often ask directly about the cue validity probability [e.g., "There is an animal that lays eggs. What is the probability that it is a robin?"; @Khemlani2012], though in the broader literature on semantic memory a *free production* paradigm is often employed [e.g., "X lays eggs. What do you think X is?"; @Cree2006]. 
We found that these different ways of estimating cue validity diverge for a number of key cases, possibly due to an experimenter demand effect in the direct question paradigm.
We thus used the data from the free production paradigm ($n = 100$) to estimate cue validity. 
For a detailed analysis of the different cue validity measurements and comparison to *prevalence prior derived cue validity*, see Appendix B.

<!-- It thus implicitly captures information about other categories, though cannot capture the structure that is present in the prevalence priors. -->

@@

@@

In explaining the variable endorsements of generics, we related the referent-category prevalence (e.g., the percentage of robins that lay eggs) to the endorsement of the generalization (e.g., "Robins lay eggs") via our communicative model with prior knowledge about the distribution of prevalence (e.g., the prevalence of laying eggs for different kinds of animals). 
In doing so, we used generic statements about familiar animal categories, which has long been the cleanest domain for testing semantic theories of generics by providing minimal comparison like "Robins lay eggs" vs. "... are female". 
However, modeling familiar category generics is a correlational analysis: The relevant quantities in the model were measured rather than manipulated.
We now seek to demonstrate how these quantities are causally related to endorsement, by manipulating referent prevalence (Case 2) and prevalence priors (Case 3).
In addition, we take this opportunity to highlight the generality of the theory, by performing these additional empirical tests in different domains for generalization: events and causes.

### 2018-02-22 paper/case2-habituals.Rmd
address ellens inline comments in intro and expts

Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect a speaker's expectations, not merely her observations. 
Our computational model predicts endorsement rates given a referent-prevalence $p_{fk}$. 
Does prevalence represent the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past month) or the predictive probability of the event in the near future (e.g., how often we should expect Mary to smoke next week)?
We extend our theory by measuring participants' predictions about future rates and endorsements of habituals when causal forces intervene on the world (Expt. 2c).
We then use our model to test whether habitual endorsements are based on past frequencies or future expectations.

@@

While past frequency is often a good indicator of future tendency, the future is under no obligation to mimic the past.
Does habitual language communicate probabilities in terms of past frequency or future expectations?
On one hand, speakers can only be certain about what has happened in the past.
On the other hand, language has a communicative function, and it would be useful for speakers to convey their predictions of what will be the case in the future.

People can change their behavior abruptly due to a variety of decisions and outside events.
We introduce these causal events into our minimal endorsement paradigm and measure their influence on endorsement.
<!-- that either enable or prevent future actions. -->
To provide the appropriate model-based analysis, participants in one condition make a prediction about what will be the case in the future (*predictive frequency*).
In another condition, participants decide whether or not to endorse the habitual sentence (as in Expt. 2b).
<!-- In Expt. 2d, we examine endorsements of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers. -->
We then compare two uncertain-thresholds models to each other: one which uses participants' ratings of *predictive frequency* as the object of communication and one which uses the *past frequency* (as was done for Expt. 2b).

@@

Habitual language conveys generalizations about events.
Our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account a naive interpreter's prior beliefs about the event (measured in Expt. 2a). 
Our computational model endorses statements that communicate generalizations about events with the same sensitivity to context and frequency that people exhibit (Expt. 2b \& c).
In Expt. 2b, we varied the type of event and the past frequency with which the person did the action, and found graded endorsements of the corresponding habitual sentences.
By manipulating (rather than measuring) the referent frequency with which a person does an action, we showed how alternative models were insufficient to account for the gradience in endorsement.
In particular, a fixed threshold model that has access to the same prior knowledge and uses the same information-theoretic decision rule as our uncertain-threshold model is unable to make different predictions for different frequencies.
Only our uncertain threshold model was able to precisely account for the wide range of endorsements.

@@

<!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->
<!-- In Experiment 3, we looked at interpretations of habitual statements about different events and again found substantial gradedness that our theory provided the most parsimonious account of. -->
<!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
In Expt. 2c, we further investigated the nature of the underlying prevalence scale by introducing causal information that enabled and preventative future occurrences of the action.
We used the empirically-measured predicted future frequency as the object of communication for our endorsement model.
We found that the endorsement model that seeks to communicate its predictions (rather than its observations) is a better model of habitual endorsements under these situations.
Predicted prevalence thus captures the influence of top-down moderators (e.g., intervening causal forces) on endorsement.
<!-- To our knowledge, the experiments presented here are first empirical investigations into endorsements of habitual sentences and the first test of a formal psychological model of such generalizations in language. -->

>>>>

Finally, if habituals (and generics) are truly language for conveying generalizations, it would be useful for them to reflect speakers' expectations, not merely their observations. 
Our computational model predicts endorsement rates given a referent-prevalence $p_{fk}$. 
Does prevalence represent the actual, past frequency of the event (e.g., how often Mary has actually smoked in the past month) or the predictive probability of the event in the near future (e.g., how often we should expect Mary to smoke next week)?
We extend our theory by measuring participants' predictions about future rates and endorsements of habituals when causal forces intervene on the world (Expt. 2c).
We then use our model to test whether habitual endorsements are based on past frequencies or future expectations.

@@

While past frequency is often a good indicator of future tendency, the future is under no obligation to mimic the past.
Does habitual language communicate probabilities in terms of past frequency or future expectations?
On one hand, speakers can only be certain about what has happened in the past.
On the other hand, it is important for speakers to be able to convey their predictions of what will be the case in the future.

People can change their behavior abruptly due to a variety of decisions and outside events.
We introduce these causal events into our endorsement paradigm to measure their influence on endorsement.
<!-- that either enable or prevent future actions. -->
To provide the appropriate model-based analysis, participants in one condition make a prediction about the future (*predictive frequency*).
In another condition, participants decide whether or not to endorse the habitual sentence (as in Expt. 2b).
<!-- In Expt. 2d, we examine endorsements of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers. -->
We then compare two uncertain-thresholds models: one which uses participants' ratings of *predictive frequency* as the object of communication and one which uses the *past frequency* (as was done for Expt. 2b).
In addition, we compare to baseline linear model that uses only the *predictive frequency* (no priors) to model endorsement.

@@

Habitual language conveys generalizations about events.
Our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account a naive interpreter's prior beliefs about the event (measured in Expt. 2a). 
Our computational model endorses statements that communicate generalizations about events with the same sensitivity to context and frequency that people exhibit (Expt. 2b \& c).
In Expt. 2b, we varied the type of event and the past frequency with which the person did the action, and found graded endorsements of the corresponding habitual sentences.
By manipulating (rather than measuring) the referent frequency, we showed how alternative models were unable to account for the gradience in endorsement.
In particular, we show that prior knowledge in an information-theoretic, communicative model is not sufficient to produce gradience in endorsement: The fixed-threshold model, which has these components, does not make different predictions for different frequencies.
Only our uncertain threshold model was able to precisely account for the wide range of endorsements.

@@

<!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->
<!-- In Experiment 3, we looked at interpretations of habitual statements about different events and again found substantial gradedness that our theory provided the most parsimonious account of. -->
<!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
In Expt. 2c, we further investigated the nature of the underlying prevalence scale by introducing causal information that enabled and prevented future occurrences of the action.
We used the empirically-measured predicted future frequency as the object of communication for our endorsement model.
We found that the endorsement model that seeks to communicate its predictions (rather than its observations) is a better model of habitual endorsements under these situations.
Predicted prevalence thus captures the influence of top-down moderators (e.g., intervening causal forces) on endorsement.
<!-- To our knowledge, the experiments presented here are first empirical investigations into endorsements of habitual sentences and the first test of a formal psychological model of such generalizations in language. -->

### 2018-02-22 paper/case3-causals.Rmd
address ellens inline comments in intro and expts

```{r causalExpt, fig.cap="Overview of Experiment 3. A-C: Results of previous experiments are shown one at a time, described in text and displayed in a table. One of the results was lost. Participants are asked to review previous results once all displayed. B: Prior elicitation task: Participants predict the results of the next 5 experiments. D: Causal endorsement task: Results of previously lost experiment are found and participants are asked to evaluate the causal generalization.", fig.width = 10}
caus.exp.1 <- ggdraw() + draw_image("figs/causal-expt-1.jpeg", scale = 1) +
  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
caus.exp.2 <- ggdraw() + draw_image("figs/causal-expt-2.jpeg", scale = 1)+
  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
caus.exp.3 <- ggdraw() + draw_image("figs/causal-expt-3.jpeg", scale = 1)+
  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
caus.exp.4 <- ggdraw() + draw_image("figs/causal-expt-prior.jpeg", scale = 1)
caus.exp.5 <- ggdraw() + draw_image("figs/causal-expt-endorse.jpeg", scale = 1)

@@

```{r figure-causals-endorsement, fig.width=7, fig.height=3.5, cache = T}
figure.causals.endorsement <- bind_rows(
  m.cas.fullmodel.endorsement %>%
    mutate(src = "model"),
  d.caus.endorse.summary %>%
    select(distribution, frequency, MAP_h, low, high) %>%
    rename(dist = distribution, MAP = MAP_h, cred_lower = low, cred_upper = high) %>%
    mutate(src = 'data')
) %>%
  ungroup() %>%
  mutate(
    src = factor(src, levels = c( "model", "data")),
    dist = factor(dist, 
           levels = c("rare_weak", "common_weak", "rare_deterministic","common_deterministic"),
           labels = c(
                       "Weak, Rare", "Weak, Common","Strong, Rare","Strong, Common"))
    ) %>%
  ggplot(., aes( x = frequency, y = MAP, ymin = cred_lower, ymax = cred_upper, 
                 color = dist, #linetype = dist, 
                 shape = dist,
                        group = dist#, 
                 #alpha = src
                 ))+
  #geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
  geom_linerange(position = position_dodge(8), alpha = 1, alpha=0.8)+
  geom_line(position = position_dodge(8), alpha = 0.8, linetype = 3)+
  geom_point(position = position_dodge(8), size = 2.25)+
  #theme(axis.text.x = element_text(angle = 90))+
  #geom_hline(yintercept = 0.5, lty = 2, color = 'black', alpha = 0.4)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_alpha_manual(values = c(1, 0.3))+
  scale_x_continuous(limits = c(10, 90), breaks = c(20, 70))+
  #scale_fill_solarized()+
  scale_color_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
  xlab("Referent prevalence")+
  ylab("Causal Endorsement")+
  facet_grid(.~src)+
  #coord_flip()+
  coord_fixed(ratio = 90)+
  #guides(fill = F)+
  guides(
    shape=guide_legend(title="Background distribution"),
    color=guide_legend(title="Background distribution")
    )+
  theme(
    plot.margin = unit(c(0,6,0,6), "pt")
    #legend.position = 'bottom', 
    # legend.direction = 'horizontal', 
    # legend.title = element_blank()
  )
```

```{r figure-causals, fig.width=9, fig.height=4, cache = T, fig.cap="Endorsing generalizations about causes. A: Endorsement model predictions (left) and human elicited endorsements (right) for four background distributions and two observed frequencies. B: Prevalence prior distributions and interpreter model posteriors upon hearing a causal generalization, for the experimentally manipulated priors. Vertical lines denote referent-prevalence levels for the causal endorsement task. Endorsement mode predictions, interpreter model posteriors, and prevalence priors are inferred using both Expt. 3a and 3b data, following the same Bayesian data analytic approach outlined in Appendix C."}

>>>>

```{r causalExpt, fig.cap="Overview of Experiment 3. A-C: Results of previous experiments are shown one at a time, described in text and displayed in a table. One of the results was lost. Participants are asked to review previous results once all displayed. B: Prior elicitation task: Participants predict the results of the next 5 experiments. D: Causal endorsement task: Results of previously lost experiment are found and participants are asked to evaluate the causal generalization.", fig.width = 10, cache=F}
caus.exp.1 <- ggdraw() + draw_image("figs/causal-expt-1.jpeg", scale = 1) +
  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
caus.exp.2 <- ggdraw() + draw_image("figs/causal-expt-2.jpeg", scale = 1)+
  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
caus.exp.3 <- ggdraw() + draw_image("figs/causal-expt-3.jpeg", scale = 1)+
  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
caus.exp.4 <- ggdraw() + draw_image("figs/causal-expt-prior.jpeg", scale = 1)
caus.exp.5 <- ggdraw() + draw_image("figs/causal-expt-endorse.jpeg", scale = 1)

@@

```{r figure-causals-endorsement, fig.width=7, fig.height=3.5, cache = F}
figure.causals.endorsement <- bind_rows(
  m.cas.fullmodel.endorsement %>%
    mutate(src = "model"),
  d.caus.endorse.summary %>%
    select(distribution, frequency, MAP_h, low, high) %>%
    rename(dist = distribution, MAP = MAP_h, cred_lower = low, cred_upper = high) %>%
    mutate(src = 'data')
) %>%
  ungroup() %>%
  mutate(
    src = factor(src, levels = c( "model", "data")),
    dist = factor(dist, 
           levels = c("rare_weak", "common_weak", "rare_deterministic","common_deterministic"),
           labels = c(
                       "Weak, Rare", "Weak, Common","Strong, Rare","Strong, Common"))
    ) %>%
  ggplot(., aes( x = frequency, y = MAP, ymin = cred_lower, ymax = cred_upper, 
                 color = dist, #linetype = dist, 
                 shape = dist,
                        group = dist#, 
                 #alpha = src
                 ))+
  #geom_bar(stat='identity', position = position_dodge(), width = 0.3, color = 'black')+
  geom_linerange(position = position_dodge(8), alpha = 1, alpha=0.8)+
  geom_line(position = position_dodge(8), alpha = 0.8, linetype = 3)+
  geom_point(position = position_dodge(8), size = 2.25)+
  #theme(axis.text.x = element_text(angle = 90))+
  #geom_hline(yintercept = 0.5, lty = 2, color = 'black', alpha = 0.4)+
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.5, 1))+
  scale_alpha_manual(values = c(1, 0.3))+
  scale_x_continuous(limits = c(10, 90), breaks = c(20, 70))+
  #scale_fill_solarized()+
  scale_color_manual(values = c("#859900","#d33682","#dc322f", "#268bd2"))+
  xlab("Referent prevalence")+
  ylab("Causal Endorsement")+
  facet_grid(.~src)+
  #coord_flip()+
  coord_fixed(ratio = 90)+
  #guides(fill = F)+
  guides(
    shape=guide_legend(title="Background distribution"),
    color=guide_legend(title="Background distribution")
    )+
  theme(
    plot.margin = unit(c(0,6,0,6), "pt")
    #legend.position = 'bottom', 
    # legend.direction = 'horizontal', 
    # legend.title = element_blank()
  )
```

```{r figure-causals, fig.width=9, fig.height=4, cache = F, fig.cap="Endorsing generalizations about causes. A: Endorsement model predictions (left) and human elicited endorsements (right) for four background distributions and two observed frequencies. B: Prevalence prior distributions and interpreter model posteriors upon hearing a causal generalization, for the experimentally manipulated priors. Vertical lines denote referent-prevalence levels for the causal endorsement task. Endorsement mode predictions, interpreter model posteriors, and prevalence priors are inferred using both Expt. 3a and 3b data, following the same Bayesian data analytic approach outlined in Appendix C."}

### 2018-02-22 paper/comgen-paper.Rmd
address ellens inline comments in intro and expts

What we are left with is hybrid theories, which try to classify different kinds of generalizations and the various inferences they support [@Prasada2013].
But insofar as there is a single class of linguistic expressions that convey generalization, there should be something common to them all: a general, unified semantic core.
In this paper, we propose such a semantic core for the language of generalization.
To do so, we look to probability, the universal currency of belief and a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
However, it is not possible to develop a single cut-off for when the generalization should hold, due to examples like "Birds lay eggs" vs. "Birds are female".
Instead, we posit that the cut-off is *underspecified* in the literal meaning of a generalization, and that listeners' background knowledge and the communicative context can be used to derive more precise interpretations in the moment. 
<!-- To formalize a model of endorsement (i.e., what makes the statements true or false), we consider the communicative function of a generalization by explicitly modeling the background knowledge a language interpreter would bring to bear when understanding generalizations. -->
With these ideas, we create an endorsement model, providing the first formal theory that makes quantitative predictions about what makes generalizations in language true or false.
The assumptions of the theory, and in turn, the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.

>>>>

What we are left with is hybrid theories, which try to classify different kinds of generalizations and the various inferences they support [@Prasada2013].
But insofar as there is a single class of linguistic expressions that convey generalization, there should be something common to them all: a general, unified semantic core.
In this paper, we propose such a semantic core for the language of generalization.
To do so, we look to probability, the universal currency of belief and a useful representation for human generalization from observations [@Shepard1987; @Tenenbaum2001].
Given that certain probabilities are the result of inductive generalization, it would make sense that these are the object of communication in the language of generalization. 
However, it is not possible to develop a single cut-off for when the generalization should hold, due to examples like "Birds lay eggs" vs. "Birds are female".
Rather than throw-out the quantitative formalization of the threshold semantics, we posit that the threhsold is *underspecified* in the literal meaning of a generalization, and that listeners' background knowledge and the communicative context can be used to derive more precise interpretations in the moment. 
<!-- To formalize a model of endorsement (i.e., what makes the statements true or false), we consider the communicative function of a generalization by explicitly modeling the background knowledge a language interpreter would bring to bear when understanding generalizations. -->
With these ideas, we create an endorsement model, providing the first formal theory that makes quantitative predictions about what makes generalizations in language true or false.
The assumptions of the theory, and in turn, the conditions under which the theory may be meaningfully tested are made explicit by its instantiation in a formal model.
